Testable normative theories

### 2020-05-20 simple.tex
Added Unrestricted interpretability for clarification

\subsection{Non-completeness}
\begin{definition}[Model completeness]
	$\forall \phi \in \Phi: \phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$.
\end{definition}
\begin{definition}[Deliberation completeness]
	$\forall \phi \in \Phi: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
\end{definition}
\begin{proposition}
	Under Normative adequacy, Model completeness implies Deliberation completeness.
\end{proposition}
Models as defined here do not mandate Model completeness. This is good for two reasons. First, even the weaker Deliberation completeness can appear too strong. Second, it is dubious that, for non trivial decision problems, models can be found for which both Normative adequacy is normatively compelling and Model completeness holds.

>>>>

\subsection{Non-completeness}
\begin{definition}[Model completeness]
	$\forall \phi \in \Phi: \phi \in \Box\Phi \lor ¬\phi \in \Box\Phi$.
\end{definition}
\begin{definition}[Unrestricted interpretability]
	$\forall \phi \in \Phi: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
\end{definition}
\begin{definition}[Deliberation completeness]
	$\forall \phi \in \Phi: \phi \in \iPhi \lor ¬\phi \in \iPhi$.
\end{definition}
The following proposition directly follows from the definitions.
\begin{proposition}
	1) Under Normative adequacy, Model completeness implies Deliberation completeness. 2) Unrestricted interpretability implies Deliberation completeness. 3) Under No contradiction, Unrestricted interpretability is equivalent to Deliberation completeness.
\end{proposition}
Models as defined here do not mandate Model completeness. This is good for two reasons. First, even the weaker Deliberation completeness can appear too strong. Second, it is dubious that, for non trivial decision problems, models can be found for which both Normative adequacy is normatively compelling and Model completeness holds.
